How much gut content data is required to predict trophic interactions?

### 2022-06-20 manuscript/ms_C2/ms_C2.tex
Incorporated most comments from Guy, Eoin and David

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

\title{Optimal amount of gut content data required to predict trophic
interactions using a food web model}

\author{
    Anubhav Gupta
    \thanks{Corresponding author}
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:anubhav.gupta@ieu.uzh.ch}{\nolinkurl{anubhav.gupta@ieu.uzh.ch}}} \\
   \And
    Eoin O' Gorman
   \\
    School of Life Sciences \\
    University of Essex \\
  CO4 3SQ Colchester, UK \\
  \texttt{\href{mailto:e.ogorman@essex.ac.uk}{\nolinkurl{e.ogorman@essex.ac.uk}}} \\
   \And
    Owen L. Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
  }

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{lineno}
\linenumbers
\usepackage {amsmath}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing

\begin{document}
\maketitle

\def\tightlist{}

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
\item
\item
\item
\end{enumerate}
\end{abstract}

@@

\hypertarget{alternate-titles}{%
\section{Alternate titles}\label{alternate-titles}}

\begin{itemize}
\item
  Predicting trophic interactions using incomplete gut content data
\item
  Effect of the amount of gut content data on the accuracy and precision
  of food web prediction
\end{itemize}

@@

Knowledge about the trophic interactions in a food web is crucial in
ecology from identifying keystone species (Jord'an 2009) to quantifying
robustness of a food web to species extinctions (Dunne, Williams, and
Martinez 2002). This has led to the development of numerous food web
models (Allesina, Alonso, and Pascual 2008; Cohen, Newman, and Steele
1985; Gravel et al. 2013; Petchey et al. 2008; Tamaddoni-Nezhad et al.
2013). Along with inferring missing links in an observed food web, the
food web models are also used for ecological forecasting (Hattab et al.
2016; Lindegren et al. 2010) and understanding the underlying mechanism
governing the interactions in a food web (O'NAGorman et al. 2019).

Although food web models are constructed using prior theory governing
the food webs, interaction data is required to parameterise a model. For
example, Petchey et al. (2008) used presence-absence information about
trophic interactions to parameterise the allometric diet breadth model
and thereby predict species interactions. These information can be
inferred from diverse set of methods such as gut content analysis
(Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017), stable isotope
ratio analysis of tissues (Layman et al. 2007), experimentation (Warren
1989), DNA metabarcoding (Roslin and Majaneva 2016) and literature
research (Gray et al. 2015; Cohen and Mulder 2014; Goldwasser and
Roughgarden 1993). All of these methods can infer the diet of a
consumer, however different methods measure different consumed
components, thereby resulting in different levels of uncertainty in the
inferred diet (citreqd). A single gut content of a predator describes
what that individual has consumed recently which can be used to infer
the diet of the predator (Eitzinger et al. 2018; O'NAMalley et al. 2017;
Dixon et al. 2017; McClain-Counts, Demopoulos, and Ross 2017;
Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017). Stable isotope
data when combined with mixing models can be used to determine which
prey items are most likely fed upon by a predator (Kadoya, Osada, and
Takimoto 2012; Crawford, Mcdonald, and Bearhop 2008).

Acquiring food web data from these methods is time consuming and
expensive (reference). For example, many gut content data needs to be
collected to infer the complete presence-absence information of a food
web structure with high accuracy and precision. Also further time and
resource investment is required to process the collected samples. Hence,
there is an utmost demand to know the minimum number of presence-absence
information of a food web to parameterise a food web model with high
accuracy and high precision, so that one knows when to stop collecting
any further data on the food web.

The key question we are interested in answering is how much
presence-absence information is required to infer food web structure
from a food web model with high accuracy and high precision. In other
words, in case of gut content data how many samples of gut content
should one collect from the field to parameterise a food web model? To
answer this question, we use the presence-absence information from gut
content data, and allometric diet breadth model (ADBM) to predict
trophic interactions. We parameterise the model using approximate
Bayesian computation/rejection Monte Carlo sampling.

@@

In the upcoming sections, we present the allometric diet breadth model
(ADBM) and the gut content data used to infer trophic interactions. We
also give a detailed account of using partial gut content data to
parameterise the ADBM using approximate Bayesian computation (ABC). We
assessed model predictions using true skill statistic and various
structural food web properties for comparison across food webs.

@@

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency foraging model (MacArthur and
Pianka 1966). The ADBM predicts the set of prey species a consumer
should feed upon to maximise its rate of energy intake (Petchey et al.
2008). The foraging variables in the model: energy content of the
resources, handling times of the prey, space clearance rate and prey
densities are allometrically scaled to the body sizes of the species.

\hypertarget{broadstone-stream}{%
\subsection{Broadstone Stream}\label{broadstone-stream}}

Broadstone Stream (51\(^\circ\) 05' N 0\(^\circ\) 03' E; 120 m above
sea-level) is a second-order tributary of the River Medway in south-east
England. It is dominated by invertebrates as the acidity of the stream
(pH 4.7-6.6) excludes fish. The stream consists of 25 common
invertebrate species (Woodward, Speirs, and Hildrew 2005a). Among the
predators, the three large species are \emph{Cordulegaster boltonii}
Donovan, \emph{Sialis fuliginosa} Pict. and \emph{Plectrocnemia
conspersa} {[}Curtis{]} and the three small species are the larvae of
the tanypod midges \emph{Macropelopia nebulosa} {[}Meigen{]},
\emph{Trissopelopia longimana} {[}Staeger{]}, and \emph{Zavrelimyia
barbatipes} {[}Kieffer{]}. Broadstone Stream food web is one of the most
completely described food webs available for any system (J. M.
Schmid-Araya et al. 2002; Hildrew 2009; Layer et al. 2010; and Woodward,
Speirs, and Hildrew 2005b).

\hypertarget{celtic-sea}{%
\subsection{Celtic Sea}\label{celtic-sea}}

The Celtic Sea is an area of continental shelf bordered by Ireland, the
UK and the Bay of Biscay. Precise sampling locations and dates were not
given in the Barnes et al.~(2008) dataset, from where the data used in
this chapter were extracted, so we pooled data over the whole time
period and locations to capture general patterns. Only locations
consistently sampled through the 1987--2001 time series were used
(Blanchard et al., 2005).

The feeding links of fishes in the Celtic Sea have been described in a
published global dataset of individual predator and prey body sizes and
taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29
predator species were included in the food web presented here. The
original stomach contents data were collected from dissections carried
out on board research vessels during the annual surveys carried out by
the Centre for Environment, Fisheries and Aquaculture Science (Cefas)
(Pinnegar et al., 2003). Predator and prey length were recorded and
converted to body mass by Barnes et al.~(2008) using published
regression equations. Only vertebrate prey were identified and measured,
with the vast majority being identified to species.

\hypertarget{afon-hirnant}{%
\subsection{Afon Hirnant}\label{afon-hirnant}}

The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K.
(52\(^\circ\) 52'N 03\(^\circ\) 34) with the study being conducted at
three sites. The pH within each site ranged from about 5.5 to 7 over the
course of the year.

A total of 180 invertebrate samples were collected for the whole
sampling periods. All individuals within the benthic samples were
counted and identified to the lowest possible taxonomic level (usually
species). Prey items were identified using a combination of taxonomic
keys and reference slides of previously identified species, after Jenny
M. Schmid-Araya et al. (2002); J. M. Schmid-Araya et al. (2002).

\hypertarget{tadnoll-brook}{%
\subsection{Tadnoll Brook}\label{tadnoll-brook}}

Description of Tadnoll Brook here

\hypertarget{coilaco}{%
\subsection{Coilaco}\label{coilaco}}

Description of Coilaco here

\hypertarget{guampoe}{%
\subsection{Guampoe}\label{guampoe}}

Description of Guampoe here

\hypertarget{trancura}{%
\subsection{Trancura}\label{trancura}}

Description of Trancura here

\hypertarget{food-web-construction}{%
\subsection{Food web construction}\label{food-web-construction}}

Presence and absence interactions of food web data can be aggregated in
different ways (Gilljam et al. 2011). A common way of aggregating food
web data is the taxonomic approach, where a species is defined as
predating on another if at least one prey species individual was found
in the gut of a predator species individual. Whereas in size-class food
web, a feeding link was assigned if at least one prey item within a size
class was found in the gut of a predator of another size class,
irrespective of their taxonomy. In our study, we aggregate the food web
on the basis of size class.

@@

The accuracy of the predicted diet of the predators was defined using
true skill statistic (TSS) which takes into account the true and false
predictions of both the presence and absence of links defined as:

\[ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} \] where \(a\) is the number of
observed links that are predicted by the model (true positives), \(d\)
is the number of observed absences of links that are correctly predicted
(true negatives), \(b\) is the number of false positives, and \(c\) is
the number of false negatives.

The \(TSS\) ranges from \(-1\) to \(1\), where +1 indicates a perfect
prediction. A \(TSS\) value of zero or less indicates a performance no
better than random (Allouche, Tsoar, and Kadmon 2006).

@@

From a pool of gut content data, we draw a set of gut content data
randomly. Then we used the rejection ABC to accept a parameter value
from a prior distribution which would have resulted in the minimum
distance, where distance = 1 - True skill statistic. The true skill
statistic was computed between the predators' diet predicted from the
ADBM, and that from the sampled gut content data. We repeated this
process for \(n~(= 100)\) number of times for every \(i\) number of
guts, where \(i\) lies between 1 and total number of gut content data in
the pool.

@@

\begin{itemize}
\item
  Predators \(P: P = \{p_1, p_2, \dots, p_k \}\)
\item
  A pool of gut content data \(G: G = \{g_1, g_2, \dots, g_n\}\), where
  \(g_{n}\) is a one-dimensional matrix containing ones and zeros.
\item
  A model prediction
  \(model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\),
  where \(d_{p_k}\) is a one-dimensional diet matrix of predator \(k\)
  containing ones and zeros.
\item
  A summary statistic \(s(x): s(x) \subseteq model(\theta)\)
\item
  A distance function \(d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)\)
\item
  An observed food web
  \(Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}\)
\end{itemize}

@@

A prediction interval containing \(TSS\) between observed and predicted
food webs for every \(i\) number of gut content data drawn from the pool
of gut content data.

@@

We first present how the accuracy of the food web model vary in
predicting trophic interactions when we increase the amount the gut
content data provided to the food web model. Then, we calculate the
number of gut content data for each food webs corresponding to which the
accuracy results in 90\% of the maximum true skill statistics predicted
by the food web model. We also compute the goodness of the food web
model in predicting structural properties from incomplete gut content
data. We did that by computing mean standardised error in food web
properties.

@@

{\centering \includegraphics[width=500px]{../../results/misc/plot_min_gut_vs_X}

@@

\hypertarget{references}{%
\section{References}\label{references}}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

\title{How much gut content data is required to predict trophic
interactions?}

\author{
    Anubhav Gupta
    \thanks{Corresponding author}
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:anubhav.gupta@ieu.uzh.ch}{\nolinkurl{anubhav.gupta@ieu.uzh.ch}}} \\
   \And
    Eoin O' Gorman
   \\
    School of Life Sciences \\
    University of Essex \\
  CO4 3SQ Colchester, UK \\
  \texttt{\href{mailto:e.ogorman@essex.ac.uk}{\nolinkurl{e.ogorman@essex.ac.uk}}} \\
   \And
    Other authors
   \\
    XXX XXX \\
    XXX XXX \\
  XXX XXX \\
  \texttt{XXX XXX} \\
   \And
    Owen L. Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
  }

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{lineno}
\usepackage {amsmath}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing
\begin{document}
\maketitle

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  One of the biggest obstacles in food web ecology is the time and
  effort required to adequately describe the structure of a food web
  using gut content data. Food web models such as the ADBM can be used
  to circumvent this problem by predicting the interactions based on
  easily measured characteristics, such as the size of organisms.
  However, presence-absence data such as gut content data is required to
  parameterise these food web models. And collecting and analysing these
  data from the field is an expensive and time consuming task.
  Therefore, it is crucial to know how much gut content data is required
  to parameterise food web models with high accuracy and high precision.
\item
  Here, we explore seven food webs in the literature and determine how
  much gut content data would be needed to accurately predict their
  structure using the ADBM. We use Bayesian computation to parameterise
  the ADBM, and true skill statistics to measure the goodness of fit,
  and do so while varying the amount of gut content data used in the
  parameterisation.
\item
  We estimated the minimum amount of gut content data required for seven
  different food webs that resulted in 95\% of the maximum true skill
  statistics achieved by the ADBM when all available gut content data
  was used. We found that incomplete gut content data can be used to
  parameterise the ADBM with the lowest amount of gut content data being
  28\% of the available gut content data.
\item
  These results suggest that one need not collect such a large quantity
  of gut content data to predict the structure of a food web, thereby
  reducing sampling effort considerably, while having little effect on
  precision or accuracy of predictions.
\end{enumerate}
\end{abstract}

@@

@@

Knowledge about the trophic interactions in a food web is crucial in
ecology for purposes ranging from identifying keystone species (Jord'an
2009) to quantifying robustness of a food web to species extinctions
(Dunne, Williams, and Martinez 2002). This has led to the development of
numerous food web models (Allesina, Alonso, and Pascual 2008; Cohen,
Newman, and Steele 1985; Gravel et al. 2013; Petchey et al. 2008;
Tamaddoni-Nezhad et al. 2013). Along with inferring missing links in an
observed food web, the food web models are also used for ecological
forecasting (Hattab et al. 2016; Lindegren et al. 2010) and for
understanding the underlying mechanism governing the interactions in a
food web (Gorman et al. 2019).

Although food web models are constructed using prior theory about the
factors that determine trophic interactions, empirical data about
interactions is required to parameterise a model. For example, Petchey
et al. (2008) used presence-absence information about trophic
interactions to parameterise the allometric diet breadth model and
thereby predict species interactions. These empirical information about
interactions can come from diverse set of methods such as gut content
analysis (Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017),
stable isotope ratio analysis of tissues (Layman et al. 2007),
experimentation (Warren 1989), DNA metabarcoding of gut contents or
faeces (Roslin and Majaneva 2016) and literature research (Gray et al.
2015; Cohen and Mulder 2014a; Goldwasser and Roughgarden 1993a).

Each of these sources of information about trophic interactions has
shortcomings. For example: Stable isotope ratio analysis of the
organism's tissue does not give direct information of the diet of that
organism but rather gives approximate trophic position of that species
in the food web (Wada, Mizutani, and Minagawa 1991; Jennings and van der
Molen 2015). Although mixing models can be used to determine what prey
items are most likely fed upon by a predator, this results in
uncertainty in the estimates (Kadoya, Osada, and Takimoto 2012;
Crawford, Mcdonald, and Bearhop 2008). Similarly, DNA metabarcoding
could have issues in detecting secondary predation or cannibalism
(Pompanon et al. 2012; Nielsen et al. 2018) and is prone to
environmental contamination (e.g.~DNA in the water swallowed along with
DNA from an aquatic consumer's prey cannot be differentiated from actual
prey) (Kelly et al. 2014). Furthermore, construction of food webs via
literature review can lead to false positives--links included when in
reality no link would occur because it makes an assumption that the
species interactions inferred from a system will occur in another system
as well(Gray et al. 2015; Cohen and Mulder 2014b; Goldwasser and
Roughgarden 1993b).

Nielsen et al. (2018) have shown that gut content analysis method has a
better match with real diet when compared to other methods.

Acquiring food web data from gut content analysis is time consuming and
expensive (AG: Do we need a reference? Next sentence explains the
reason.). In part this is due to the perception that many gut contents
must be collected and analysed in order to be confident that the
majority of possible trophic links among species have been observed.
Furthermore, considerable time, resource investment, and expertise is
required to process the collected samples. Hence, there is of
considerable importance to know the minimum number of gut contents and
of which consumer species that are required to parameterise a food web
model with high accuracy and high precision, so that one knows when is a
good time to stop collecting any further empirical data on the food web.

Therefore, the key question we are interested in answering is how much
presence-absence information, in the form of gut content data, is
required to infer food web structure from a food web model with high
accuracy and high precision. In other words, how many samples of gut
content should one collect from the field to parameterise a food web
model? To answer this question, we use the presence-absence information
from gut content data to parameterise the allometric diet breadth model
(ADBM) thereby predicting trophic interactions in seven different food
webs using rejection approximate Bayesian computation, where the fit of
the model was measured using true skill statistics. We computed the true
skill statistics of the predicted food webs for different number of
predator guts to calculate the minimum number of gut content data to
infer food web structure. Our study provides a guideline on how many gut
content data is required to predict food web structure using a food web
model.

@@

In the upcoming sections, we present the empirical food webs, the
allometric diet breadth model (ADBM), and the gut content data used to
infer the trophic interactions. We also give a detailed account of using
partial gut content data to parameterise the ADBM using rejection
approximate Bayesian computation (ABC). We assessed model predictions
using the true skill statistic for comparison across food webs.

\hypertarget{the-empirical-food-webs}{%
\subsection{The Empirical Food Webs}\label{the-empirical-food-webs}}

In our study, we used food webs for which gut content data is available
at an individual level and data that is or that we could make FAIR
(Wilkinson et al. 2016). Presence and absence interactions of food web
data can be aggregated in different ways (Gilljam et al. 2011). A common
way of aggregating food web data is the taxonomic approach, in which
nodes in the food web are taxa (e.g.~species), or life stages of taxa,
and one species is said to feed on another species if at least one
individual of the latter is found in at least one gut of the former.
Another approach is based on size, rather than taxonomy, and in this the
nodes in the food web are size classes. Here, a feeding link occurs
between two size classes if at least one prey item within a size class
was found in the gut of another size class, irrespective of their
taxonomy.

In our study, we aggregate the gut content data on the basis of size
class because the food webs constructed using this approach were better
predicted by the ADBM compared to the taxonomic approach (Woodward et
al. 2010a), and this is because the ADBM is based on foraging rules
defined using the body sizes of organisms (Petchey et al. 2008).

Our study is based on the assumption that the food web constructed using
the complete gut content data is the true food web. However, this might
not be the case because the links are still under-sampled for many nodes
(Woodward et al. 2010b). This could result in a lower true skill
statistic (TSS) of the predicted food web from the ADBM, which can
result in a biased estimate of the minimum number of gut content data
required to achieve 95\% of the TSS achieved using complete gut content
data.

In the following sections 2.1.1-2.1.5, we briefly explain seven
empirical food webs used in our study. The text used in those sections
are paraphrased from Gilljam et al. (2011).

\hypertarget{broadstone-stream}{%
\subsubsection{Broadstone Stream}\label{broadstone-stream}}

Broadstone Stream (51\(^\circ\) 05' N 0\(^\circ\) 03' E; 120 m above
sea-level) is a second-order tributary of the River Medway in south-east
England. At the time of sampling in 1996--1997, the stream was acidic
(pH 4.7--6.6) and fishless. About 31 common species make up the
macroinvertebrate food web, including six major predators and
detritivores like stoneflies and chironomids (Woodward, Speirs, and
Hildrew 2005).

Between June 1996 and April 1997, thirty randomly scattered benthic
Surber sample-units (25cm \(\times\) 25cm quadrat; mesh aperture 330mm)
were taken every two months and kept in 5\% formalin. All individuals
retrieved from the benthos and identified in stomach contents had their
linear body dimensions quantified and converted to dry mass using known
regression formulae (listed in Woodward and Hildrew (2002)).

The predators' foreguts were dissected and analysed with 400
magnification in the Surber samples. The individual body masses of eaten
prey were calculated using the same methods as for the benthic samples,
using reference slides as a guide (Woodward, Speirs, and Hildrew 2005).
Over the six sample instances, a single dataset was produced. Each
predator and prey individual involved in a feeding relationship was
measured and converted into their respective body masses, resulting in a
total of 2893 individuals.

\hypertarget{celtic-sea}{%
\subsubsection{Celtic Sea}\label{celtic-sea}}

The Celtic Sea is a continental shelf area that is bounded by Ireland,
the United Kingdom, and the Bay of Biscay. Because the Barnes et al.
(2008) dataset, from which the data utilised in this chapter were taken,
did not provide precise sampling sites and dates, the data was pooled
throughout the whole time period and locations to capture broad
tendencies. Only places that were sampled consistently from 1987 to 2001
were used (Blanchard et al. 2005).

In a published global dataset of individual predator and prey body sizes
and taxonomy (Barnes et al., 2008), the feeding linkages of fish in the
Celtic Sea were described. The original stomach contents data were
acquired during annual surveys conducted by the Centre for Environment,
Fisheries, and Aquaculture Science (Cefas) on board research vessels
during dissections (Pinnegar et al. 2003). Barnes et al. (2008) used
known regression equations to measure predator and prey lengths and
convert them to body mass.

\hypertarget{afon-hirnant}{%
\subsubsection{Afon Hirnant}\label{afon-hirnant}}

Three sites in the Afon Hirnant, in North Wales, UK (\(52^\circ\) 52' N
\(03^\circ\) 34' W), were used for the study. The average yearly
discharge was 2.08 to 7.26 \(m^3/s\), with a pH ranging from 5.5 to 7.
(check Figueroa (2007) and Woodward et al. (2010c) for full details).
Invertebrates were collected using a Hess sampler (sampling area: 0.028
\(m^2\); mesh aperture 80 \(\mu m\)), with 15 sample-units obtained at
random at each site and season, totaling 180 samples across the sampling
period. The invertebrate fauna was promptly preserved in 100\% ethanol
and sorted in the lab. By removing predators' foreguts, which were
mounted in Euparal media and viewed at 400 magnification, feeding
interactions were determined.

Every predator's linear dimensions (for example, body length) and
individual prey items inside each predator's foregut were measured and
then translated to body mass values using published regression equations
for each taxon (presented in Woodward et al. (2010c)). If the prey items
were highly digested, the average body length of individuals in the same
family (Ephemeroptera, Plecoptera, or Trichoptera) in the habitat was
used. The body lengths of Chironomidae (Diptera) were calculated using
previously established species-specific regressions between head capsule
width and body length (Figueroa 2007).

\hypertarget{tadnoll-brook}{%
\subsubsection{Tadnoll Brook}\label{tadnoll-brook}}

The Tadnoll Brook is a tributary of the River Frome in Southern England,
UK, with a mean annual discharge of 0.35 \(m^3/s\) and a pH of 6.9--7.7.
(Edwards et al., 2009b).

A 240-m reach was sampled every two months between February and December
2005 to create the summary food web. A Surber sampler was used to
collect invertebrates every two months (0.06 m2; mesh aperture 300 mm).
20 random samples were taken on each occasion, stored in the field in
4\% (w/v) formalin, and then sorted for invertebrates. Fish were
captured with an electrofisher, anaesthetized with 2-phenoxyethanol,
recognised to species, measured, and weighed on each occasion (Woodward
et al., 2010). The guts of trout (Salmo trutta L.) with fork lengths
more than 70 mm were then flushed with a tiny manual water pump and
stored in 4\% formalin. For smaller trout and other fish species
(\emph{Cottus gobio}, \emph{Anguilla anguilla}, \emph{Phoxinus
phoxinus}, \emph{Barbatula barbatula}, \emph{Gasterosteus aculeatus}),
specimens were sacrificed and frozen for subsequent dissection.

Gut contents analysis was performed on each sample occasion for the fish
assemblage, whereas invertebrates had far less varied diets and were
only characterised in May and October. Individuals of the benthos'
numerically dominant or trophically important invertebrate taxa were
taken from the Surber samples, dissected, and the contents of the
foregut investigated for animal prey, which were recognised at
\(400\times\) magnification by comparison with reference specimens. The
taxa used to examine stomach contents covered more than 95\% of the
individuals observed in the Benthos. Wherever possible, predators' gut
contents were matched to species, and linear body dimensions were
measured. Using established regression equations, the dry mass of prey
items and invertebrate predators was calculated (Benke et al. 1999;
Ganihar 1997; Burgherr and Meyer 1997; Gonzalez, Basaguren, and Pozo
2002; Smock 1980; Edwards et al. 2009; MEYER 1989).

\hypertarget{guampoe-coilaco-and-trancura-rivers-chile}{%
\subsubsection{Guampoe, Coilaco and Trancura Rivers,
Chile}\label{guampoe-coilaco-and-trancura-rivers-chile}}

Three rivers (the Coilaco, Guampoe, and Trancura Rivers) in the
catchment area of the Tolten River in south Chile, South America, were
studied in a similar way. The Coilaco River (discharge 2.1--16.8
\(m^3/s\)), Guampoe River (output 1.8--7.5 \(m^3/s\)), and Trancura
River (discharge 8.8--49.3 \(m^3/s\)) are all pH 6.7--7.6 circumneutral
rivers (Figueroa 2007).

In each river, eight benthic samples were taken in each season between
1984 and 1985, totaling 96 sample-units for the whole sampling period
(Campos et al., 1985). Invertebrates were gathered using a Surber
sampler (sampling area: 0.09 \(m^2\); mesh aperture 250 \(\mu m\)) and
stored in 70\% ethanol before being transported to the lab for species
identification and food web analysis.

The feeding linkages were discovered by analysing the gut contents of
all individuals observed in each sample. Large invertebrates had their
guts removed and mounted in Euparal, whilst small specimens were mounted
whole and studied with \(400\times\) magnification. Following Schmid
(1993) and (Schmid-Araya et al. 2002), species prey items detected on
each gut were identified using previously mounted reference slides.
Using known regression equations (mentioned in Reiss and Schmid-Araya
(2008); Baumgärtner and Rothhaupt (2003); Miserendino (2001); Woodward
et al. (2010b)), all linear dimensions were translated to body mass
estimates.

@@

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency foraging model (MacArthur and
Pianka 1966). We chose this model for various reasons, including because
it uses the body size of organisms as input to predict feeding
interactions, and because of our familiarity with it. The ADBM predicts
the set of prey types (e.g.~species or sizes classes) a consumer should
feed upon to maximise its rate of energy intake (Petchey et al. 2008).
The foraging variables in the model are: energy content of the
resources, handling times of the prey, space clearance rate, and prey
densities. These are allometrically scaled to the body sizes of the
species. Further details on the foraging rules defined in the ADBM and
ADBM's predictive power across different food webs can be found in
Petchey et al. (2008).

@@

The accuracy of the predicted diet of the predators was measured using
true skill statistic (TSS) which takes into account the true and false
predictions of both the presence and absence of links defined as:

\[ \text{TSS} = \frac{ad-bc}{(a+c)(b+d)} \] where \(a\) is the number of
observed links that are predicted by the model (true positives), \(d\)
is the number of observed absences of links that are correctly predicted
(true negatives), \(b\) is the number of false positives, and \(c\) is
the number of false negatives. The \(TSS\) ranges from \(-1\) to \(1\),
where +1 indicates a perfect prediction. A \(TSS\) value of zero or less
indicates a performance no better than random (Allouche, Tsoar, and
Kadmon 2006).

@@

\textbf{Comment AG: Is it necessary to have the sections 1.1 and 1.2 of
the supplementary information in the Supplementary information or shall
the sections 1.1 and 1.2 be migrated to the main text (manuscript)?}

From an empirical dataset of gut content data, we take a random sample
of gut contents of specific size (see below) to create a partial gut
content dataset. We then fit the ADBM to this partial dataset.

{\centering \includegraphics[width=500px]{../../manuscript/fig/ms_C2(1)}

\caption{\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data. Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively. Red line represents the number of predator guts required to achieve a TSS of 95\% of the maximum TSS. (b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only. The dashed line shows where the ratio is one for reference.}\label{fig:unnamed-chunk-1}
\end{figure}

To fit the ADBM to a gut content dataset (be it complete or partial), we
used the rejection ABC method we previously developed in Gupta, Furrer,
and Petchey (2022) to accept a parameter value from a prior distribution
which would have resulted in the minimum distance, where distance = 1 -
True skill statistic. The true skill statistic was computed between the
diets predicted from the ADBM, and those observed in the sampled gut
content data. We repeated this process \(n~(= 100)\) times for every
\(i\) number of guts, where \(i\) lies between 1 and total number of gut
content data in the pool.

@@

\begin{itemize}
\item
  Predators \(P: P = \{p_1, p_2, \dots, p_k \}\)
\item
  A pool of gut content data \(G: G = \{g_1, g_2, \dots, g_n\}\), where
  \(g_{n}\) is the observed diet matrix containing ones and zeros.
\item
  A model prediction
  \(model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\),
  where \(d_{p_k}\) is the predicted diet matrix of predator \(k\)
  containing ones and zeros.
\item
  A summary statistic \(s(x): s(x) \subseteq model(\theta)\), where
  \(s(x)\) is the diet of some or all of the predators.
\item
  A distance function \(d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)\), which
  quantifies how close the observed diet is to the predicted diet of
  some or all of the predators.
\item
  An observed food web
  \(Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}\), where \(d_{p_k}'\)
  is the observed diet matrix of predator \(k\) containing ones and
  zeros.
\end{itemize}

@@

The \(TSS\) between observed and predicted food webs, and the posterior
parameter distributions for every \(i\) number of gut content data drawn
from the pool of gut content data.

\hypertarget{computing-the-minimum-gut-content-data}{%
\subsection{Computing the minimum gut content
data}\label{computing-the-minimum-gut-content-data}}

Using TSS of the predicted food webs for different number of predator
guts, we computed the number of gut content data that results in the
mean TSS equal to the 95\% of the mean TSS achieved by the model using
all the predator guts for a food web. We call this number of gut content
data as the minimum gut content data.

@@

We first present how the accuracy of the food web model in predicting
trophic interactions varies with increasing amount of gut content data
provided to the food web model. Then, we calculate the number of gut
content data for each food webs that results in accuracy equal to 95\%
of the maximum true skill statistics predicted by the food web model.

@@

{\centering \includegraphics[width=400px]{../../results/misc/plot_min_gut_vs_X}

@@

\hypertarget{reference}{%
\section*{Reference}\label{reference}}
\addcontentsline{toc}{section}{Reference}
